Generating a README.txt file for the Dryad submission of data from study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-18 dryad/README.Rmd
adding methodological information

---
title: 'Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life"'
output:
  pdf_document:
    keep_md: yes
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  results = 'hide'
)
```

This README file was generated on `r Sys.Date()` by Luna L. Sánchez Reyes, <https://orcid.org/0000-0001-7668-2528>

@@

DATA & FILE OVERVIEW

@@

The first biological example uses datelife on a small sample of bird species.
The second one uses datelife on bird species belonging to the family Fringillidae of "true finches", following the NCBI taxonomy.
The mock example was created by replacing species names from the small example with letters, and reducing the number of source chronograms.

@@

```{r, echo = FALSE}

csv_file_names <- c("Sanchez-Reyes_etal_2022_table_1.csv",
                    "Sanchez-Reyes_etal_2022_table_2.csv",
                    "Sanchez-Reyes_etal_2022_supplementary_table_S1.csv",
                    "Sanchez-Reyes_etal_2022_supplementary_table_S2.csv")
tre_file_names <- c("Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre")
```

```{r, echo=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv")
```

  File 1 Name: Sanchez-Reyes_etal_2022_table_1.csv    
	File 1 Description: CSV (comma separated values) file containing results from the small example. Names and ages (in Million years) of nodes from source chronograms that have been congruified to nodes of the chosen tree topology.

```{r, echo=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-small-example-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_2.csv")
```

	File 2 Name: Sanchez-Reyes_etal_2022_table_2.csv    
	File 2 Description: CSV (comma separated values) file containing a summary of node age (in Million years) data from table 1.

```{r, echo=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")

```

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.csv    
	File XXX Description: CSV (comma separated values) file containing results from the Fringillidae example. Names and ages (in Million years) of nodes from source chronograms that have been congruified to nodes of the chosen tree topology shown in Figure 4B of the manuscript.

```{r, echo=FALSE, eval=FALSE, message=FALSE}
file.copy(from = "../tables/table-fringillidae-all-congruified.pdf",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf")

```

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf    
	File XXX Description: PDF version of file Sanchez-Reyes_etal_2022_supplementary_table_S1.csv

```{r, echo=FALSE, message=FALSE, }
file.copy(from = "../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S2.csv")

```

  File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.csv    
	File XXX Description: CSV (comma separated values) file containing a summary of node age data (in Million years) from table S1.

```{r, echo=FALSE, message=FALSE}
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf")

```

  File XXX Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.pdf    
	File XXX Description: PDF file version of file Sanchez-Reyes_etal_2022_supplementary_table_S2.csv.

	File 3 Name: Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre    
	File 3 Description: Newick version of chronogram from the mock example shown in Figure 1 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 4 Name: Sanchez-Reyes_etal_2022_figure_3_chronogram_small_example.tre    
	File 4 Description: Newick version of chronogram from the small example shown in Figure 3 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 6 Name: Sanchez-Reyes_etal_2022_figure_4A_topology_finches_mrca.tre    
	File 6: Description: Newick version of topology extracted from the Open Tree of Life synthetic tree, shown in Figure 4A of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 7 Name: Sanchez-Reyes_etal_2022_figure_4B_topology_finches_ncbi.tre    
	File 7 Description: Newick version of topology extracted from the Open Tree of Life synthetic tree, shown in Figure 4B of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File 5 Name: Sanchez-Reyes_etal_2022_figure_5_chronogram_finches_example.tre    
	File 5 Description: Newick version of chronogram from the finch example shown in Figure 5 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S1.pdf    
	File XXX Description: PDf file showing results of cross validation analysis of datelife's chronogram generating functions.

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2013. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S2 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S3 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S4 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Burns et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S5 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Claramunt et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S6 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Gibb et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S7 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S8 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S9 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hooper et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S10 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S11 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S12 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S13 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S14 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Oliveros et al. 2019. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S15 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S16 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S17 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S18 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S19 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.jpg    
	File XXX Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Uyeda et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.tre    
	File XXX Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S20 (gray).

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_    
	File XXX Description:

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_    
	File XXX Description:

3. Original names and locations of files at https://github.com/LunaSare/datelifeMS1:

```
cp tables/table-fringillidae-all.pdf dryad/Supplementary_Table_S1.pdf
cp tables/table-fringillidae-all-summary.pdf dryad/Supplementary_Table_S2.pdf
cp figures/figure-cross-validation/fig-cross-validation-xy-plots-diffs.pdf dryad/Supplementary_Figure_S1.pdf
```

METHODOLOGICAL INFORMATION

Bacterial detection was performed on the ViiA7 Real-time PCR System (Thermo Fisher Scientific) using PrimeTime® qPCR primers, probes and mastermix (IDT) according to the manufacturer’s instructions. Reactions were performed using 1X PrimeTime® Gene Expression Master Mix, 1X PrimeTime®qPCR Assay and up to 10ng of DNA. Cycling conditions were 95°C for 3 minutes, 60 cycles of 95°C for 5 seconds and 60°C for 30 seconds. Amplification results were reviewed using QuantStudioTM Real-Time PCR Software version 1.1 (Thermo Fisher Scientific). Amplification of beta-actin and prostaglandin transporter (PGT) was used to determine relative abundance.

Diversity profiling was performed by AGRF (Australian Genome Research Facility, Melbourne Australia). Samples were amplified with universal primers to the V1-V3 region of the bacterial 16S gene (forward AGAGTTTGATCMTGGCTCAG; reverse GWATTACCGCGGCKGCTG). Amplicons were indexed using the Nextera XT Index Kit (Illumina, San Diego, CA, USA) followed by Paired End sequencing on a MiSeq next generation sequencer (Illumina). Paired-end reads were assembled by aligning the forward and reverse reads using PEAR1 (version 0.9.5). Primers were identified and trimmed. Trimmed sequences were processed using Quantitative Insights into Microbial Ecology (QIIME 1.8) USEARCH (version 8.0.1623) and UPARSE software. Sequences were quality filtered and sorted by abundance after removal of full-length duplicate sequences. Singletons or unique reads were discarded. Sequences were clustered and then chimera filtered using “rdp_gold” database as reference. Reads were mapped back to Operational Taxonomic Units with a minimum identity of 97% and taxonomy was assigned using the QIIME 1 default classifier, pre-trained against Greengenes database5 (Version 13_8, Aug 2013).

```{r}

var_description_1 <- c("Node names in tree topology, as defined by taxon A and taxon B",
                       "Scientific name of the first element of a taxon pair that defines a node from a tree topology",
                       "Scientific name of the second element of a taxon pair that defines a node from a tree topology",
                       "Ages of nodes defined by taxon A and taxon B, in Million years",
                       "Reference of the study that published the chronogram from which the node ages were extracted")

var_description_2 <- c("Names of nodes from the tree topology used for the dating analysis",
                       "Minimum node age, in Million years",
                       "First quartile of node age distributions, in Million years",
                       "Mean node age, in Million years",
                       "Median node age, in Million years",
                       "Third quartile of node age distributions, in Million years",
                       "Maximum node age, in Million years",
                       "Variance of node age, in Million years",
                       "Standar deviation of node age, in Million years")
```

```{r}
text <- c()
var_descriptions <- list(var_description_1, var_description_2, var_description_1, var_description_2) 
names(var_descriptions) <- csv_file_names

>>>>

---
title: 'Generating a README.txt file for the Dryad submission of data from study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life"'
output:
  pdf_document:
    keep_md: yes
    pandoc_args: --listings
    includes:
      in_header: preamble.tex
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  results = 'hide'
)
```

# Description of README file

```{r}
line0 <- paste("This README file was generated on", Sys.Date(), "by Luna L. Sánchez Reyes, <https://orcid.org/0000-0001-7668-2528>")
```

# General Information on data set

```{r}
line1 <- "

@@

"
```

# Original file names, rename

```{r, echo = TRUE}

file.copy(from = "../tables/table-fringillidae-small-example.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_1.csv")
file.copy(from = "../tables/table-fringillidae-small-example-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_table_2.csv")
file.copy(from = "../tables/table-fringillidae-all-congruified.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.csv")
file.copy(from = "../tables/table-fringillidae-all-congruified.pdf",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf")
file.copy(from = "../tables/table-fringillidae-all-summary.csv",
          to = "../dryad/Sanchez-Reyes_etal_2022_supplementary_table_S2.csv")
file.copy(from = ".../tables/table-fringillidae-all-summary.pdf",
          to = "../dryad/anchez-Reyes_etal_2022_supplementary_table_S2.pdf")
```

# Description of data files

```{r}
line2 <- "DATA & FILE OVERVIEW

@@

The first biological example uses datelife on a small sample of bird species.
The second one uses datelife on bird species belonging to the family Fringillidae of 'true finches', following the NCBI taxonomy.
The mock example was created by replacing species names from the small example with letters, and reducing the number of source chronograms.

@@

File 1 Name: Sanchez-Reyes_etal_2022_table_1.csv    
File 1 Description: CSV (comma separated values) file with node age results from datelife's small example, presented in Table 1 of the manuscript. It contains node names, taxon names defining the nodes, the corresponding node ages (in Million years), and references of source chronograms that were congruified to the chosen tree topology to extract node ages.

File 2 Name: Sanchez-Reyes_etal_2022_table_2.csv    
File 2 Description: CSV (comma separated values) file summarizing age data (in Million years) from table 1, per node. These data are presented in Table 2 of the manuscript.

File 3 Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.csv    
File 3 Description: CSV (comma separated values) file with node age results from datelife's Fringillidae example. It contains node names, taxon names defining the nodes, the corresponding node ages (in Million years), and references of source chronograms that were congruified to the chosen tree topology (shown in Figure 4B of the manuscript) to extract node ages.

File 4 Name: Sanchez-Reyes_etal_2022_supplementary_table_S1.pdf    
File 4 Description: PDF version of file Sanchez-Reyes_etal_2022_supplementary_table_S1.csv

File 5 Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.csv    
File 5 Description: CSV (comma separated values) file summarizing age data (in Million years) from table S1, per node.

File 6 Name: Sanchez-Reyes_etal_2022_supplementary_table_S2.pdf    
File 6 Description: PDF file version of file Sanchez-Reyes_etal_2022_supplementary_table_S2.csv.

File 7 Name: Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre    
File 7 Description: Newick version of chronogram from the mock example shown in Figure 1 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

File 8 Name: Sanchez-Reyes_etal_2022_figure_3_chronogram_small_example.tre    
File 8 Description: Newick version of chronogram from the small example shown in Figure 3 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

File 9 Name: Sanchez-Reyes_etal_2022_figure_4A_topology_finches_mrca.tre    
File 9 Description: Newick version of topology extracted from the Open Tree of Life synthetic tree, shown in Figure 4A of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

File 10 Name: Sanchez-Reyes_etal_2022_figure_4B_topology_finches_ncbi.tre    
File 10 Description: Newick version of topology extracted from the Open Tree of Life synthetic tree, shown in Figure 4B of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

File 11 Name: Sanchez-Reyes_etal_2022_figure_5_chronogram_finches_example.tre    
File 11 Description: Newick version of chronogram from the finch example shown in Figure 5 of the manuscript (https://www.biorxiv.org/content/10.1101/782094v2).

File 12 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S1.pdf    
File 12 Description: PDf file showing results of cross validation analysis of datelife's chronogram generating functions.

File 13 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.jpg    
File 13 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2013. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 14 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.tre    
File 14 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S2 (gray).

File 15 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.jpg    
File 15 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 16 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.tre    
File 16 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S3 (gray).

File 17 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.jpg    
File 17 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 18 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.tre    
File 18 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S4 (gray).

File 19 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.jpg    
File 19 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Burns et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 20 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.tre    
File 20 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S5 (gray).

File 21 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.jpg    
File 21 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Claramunt et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 22 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.tre    
File 22 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S6 (gray).

File 23 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.jpg    
File 23 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Gibb et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 24 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.tre    
File 24 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S7 (gray).

File 25 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.jpg    
File 25 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 26 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.tre    
File 26 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S8 (gray).

File 27 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.jpg    
File 27 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 28 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.tre    
File 28 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S9 (gray).

File 29 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.jpg    
File 29 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hooper et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 30 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.tre    
File 30 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S10 (gray).

File 31 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.jpg    
File 31 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 32 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.tre    
File 32 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S11 (gray).

File 33 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.jpg    
File 33 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 34 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.tre    
File 34 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S12 (gray).

File 35 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.jpg    
File 35 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 36 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.tre    
File 36 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S13 (gray).

File 37 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.jpg    
File 37 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 38 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.tre    
File 38 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S14 (gray).

File 39 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.jpg    
File 39 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Oliveros et al. 2019. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 40 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.tre    
File 40 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S15 (gray).

File 41 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.jpg    
File 41 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 42 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.tre    
File 42 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S16 (gray).

File 43 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.jpg    
File 43 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 44 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.tre    
File 44 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S17 (gray).

File 45 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.jpg    
File 45 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 46 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.tre    
File 46 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S18 (gray).

File 47 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.jpg    
File 47 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 48 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.tre    
File 48 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S19 (gray).

File 49 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.jpg    
File 49 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Uyeda et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 50 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.tre    
File 50 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S20 (gray).
"
```

<!--
	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_    
	File XXX Description:

	File XXX Name: Sanchez-Reyes_etal_2022_supplementary_    
	File XXX Description: 
-->

# Methods that generated the data files

```{r}
line3 <- "
METHODOLOGICAL INFORMATION

All age data and chronograms were obtained using the R package datelife v0.6.5 https://CRAN.R-project.org/package=datelife and the chronogram database OpenTreeChronograms v2022.1.28
"
```

# Individual descriptions of each data file

```{r}
var_description_1 <- c("Node names in tree topology, as defined by taxon A and taxon B.",
                       "Scientific name of the first element of a taxon pair that defines a node from a tree topology.",
                       "Scientific name of the second element of a taxon pair that defines a node from a tree topology.",
                       "Ages of nodes defined by taxon A and taxon B, in Million years.",
                       "Reference of the study that published the chronogram from which the node ages were extracted.")

var_description_2 <- c("Names of nodes from the tree topology used for the dating analysis.",
                       "Minimum node age, in Million years.",
                       "First quartile of node age distributions, in Million years.",
                       "Mean node age, in Million years.",
                       "Median node age, in Million years.",
                       "Third quartile of node age distributions, in Million years.",
                       "Maximum node age, in Million years.",
                       "Variance of node age, in Million years.",
                       "Standard deviation of node age, in Million years.")

csv_file_names <- c("Sanchez-Reyes_etal_2022_table_1.csv",
                    "Sanchez-Reyes_etal_2022_table_2.csv",
                    "Sanchez-Reyes_etal_2022_supplementary_table_S1.csv",
                    "Sanchez-Reyes_etal_2022_supplementary_table_S2.csv")
tre_file_names <- c("Sanchez-Reyes_etal_2022_figure_1_chronogram_mock_example.tre")

text <- c()
var_descriptions <- list(var_description_1, var_description_2, var_description_1, var_description_2) 
names(var_descriptions) <- csv_file_names

for (file_name in csv_file_names) {
  # read the csv file in:
  csv_data <- utils::read.csv(file = paste0("../dryad/", file_name), header = TRUE, row.names = NULL)
  # remove the column with row numbers:
  csv_data <- csv_data[,-1]
  # create the description text
  var_list <- gsub("[.]", " ", colnames(csv_data))
  var_list <- paste0("\t", var_list, ": ", var_descriptions[[file_name]])
  text <- c(text, 
            c(paste("\nDATA-SPECIFIC INFORMATION FOR:", file_name, "\n"),
              paste("1. Number of variables/columns:", ncol(csv_data), "\n"),
              paste("2. Number of cases/rows:", nrow(csv_data), "\n"),
              "3. Variable List:", var_list,
              "\n4. Missing data codes: None",
              "\n5. Abbreviations used: NA = not applicable\n"))
}

line4 <- text
```

# Writing everything to TXT file

```{r, echo = TRUE}

writeLines(text = c(line0, 
                    line1,
                    line2,
                    line3,
                    line4), con = "../dryad/README_Sanchez-Reyes_etal_2022_data.txt")
```
